### 2023-11-09 main.tex
^^

In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can still host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but where two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$) are present. As already pointed out the dual process eventually voids the graph by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$. This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}. \\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space

@@

	\Omega=\bigtimes_{x=1}^{L} \Omega_{x}

@@

The bulk is 

@@

The process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space
\begin{equation}\label{stateSpaceDUAL-Chain}	
	\widetilde{\Omega}=N_{0}^{N}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N}
whit dual generator

@@

where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundaries are absorbing, i.e. 

@@

where $0$ and $L+1$ are the extra-sites. The duality function reads
The dual process has absorbing boundaries, i.e. all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability. This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following. 
We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$. Consider an arbitrary initial configuration of $(\bm{n}(t))_{t\geq 0}$ denoted by $\bm{n}$. For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\sum_{k=1}\delta_{s_{k}}^{y_{k}}$ with $y_{k}\in\{1,\ldots,L\}$ and $s_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$. The following  equalities holds using duality relation \eqref{duality-expectation}:
		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]=\lim_{t\to\infty}\mathbb{E}_{\hat{\bm{\xi}}}\left[D(\bm{n},\bm{\xi}(t))\right]
		\sum_{i_{1}=0}^{|\hat{\xi}_{1}|}\ldots\sum_{i_{N}=0}^{|\hat{\xi}_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\hat{\xi}_{a}|-i_{a}}\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})
	\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\hat{\xi}_{a}|-i_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\hat{\bm{\xi}}\right)
are called the \textit{absorption probabilities}, i.e. the probabilities that $i_{a}$ particles of species $a$ are absorbed at $0$ and $|\xi_{a}|-i_{a}$ are absorbed at $L+1$ when time goes to infinity and starting from a configuration $\hat{\bm{\xi}}$. Here we denoted $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$.
The duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\hat{\xi}}$ is given by 
	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{k=1}^{m}n_{s_{k}}^{y_{k}}}{(\nu-m+1)}\dt
Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations among non-empty species of types $s_{k}\in\{1,\ldots,N-1\}$ situated at sites $y_{k}\in\{1,\ldots,L\}$ with $k\in \{1,\ldots,m\}$. Using \eqref{ExptationSS}, this expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known. However, these absorption probabilities fulfil some difference equations that are not easy to solve. For example, we report here the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker. 
\paragraph{One point correlations for the $\nu\geq 1$ case}
\textbf{Remark}: In case $|\alpha|=|\beta|=\nu=1$ (when the chain is integrable) we have 
\\ Already for two-point correlations the computations become more involving and hard to solve.

@@

	\mathcal{L}^{rd}=\mathcal{L}_{\text{right}}^{rd}\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\mathcal{L}_{\text{right}}^{rd}

@@

The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values are considered at site $L+1$. \\ \\
\textbf{Remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{\text{left}}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}. 
For arbitrary site $x\in \{1,\ldots,L\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{1,\ldots,N-1\}$ reads
Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{1,\ldots,N-1\}$

@@

	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{c}^{x}-n_{\alpha}^{x})
where with the symbol $\Delta_{L}$ we denote the discrete Laplacian operator on the chain, i.e. $\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$.
Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{1,\ldots,N-1\}$ 

@@

where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu$. These average occupations evolve according to the Master equation

@@

\subsubsection{Reversible measure for the reaction-diffusion process} 
The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
	\Lambda_{rev}=\bigtimes_{x=1}^{L}\Lambda_{rev}^{x}
when for any $a\in\{1,\ldots,N\}$
\begin{equation}\label{reversibilityConditionRD}
	\alpha_{a}=\beta_{a}\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{1,\ldots,N-1\}
This measure has marginals $\Lambda_{rev}^{x}$ given by 
	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)
	p=p_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
Namely,
	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundaries. For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{g_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}}\cdots \rho_{N}^{n_{N}^{x}+n_{N}^{x+1}}
		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{x+1}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots (n_{b}^{x+1}-1)!\cdots (n_{g_{c}(a)}^{x+1}+1)!\ldots n_{N}^{x+1}!}
		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}+1}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}+1}
that simplifies to 

@@

$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{abs-dual-boundary-chain}, with the choice of the reservoirs parameters \eqref{boundaryParamRD}.

@@

We need to prove that, for arbitrary $x\in\{1,\ldots,L\}$
	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}
but it is enough of showing 

@@

 We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x+1})$. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 

@@

	&\left[\left(\sum_{d=1}^{N-1}E_{dN}^{x}\otimes\sum_{k=1}^{N-1}E_{kN}^{x+1}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{x+1} -E_{aa}^{x}\otimes E_{bb}^{x+1}\right)\right]

@@

	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)N}-E_{g_{c}(b)N}^{x}\delta_{ad})-(E_{da}^{x}\delta_{aN}-E_{aN}^{x}\delta_{da})\right)\right. \\ \otimes&\left. \left((E_{kb}^{x+1}\delta_{g_{c}(a)N}-E_{g_{c}N}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{bN}-E_{bN}^{x+1}\delta_{kb})\right)\right\}
	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)N}^{x}-E_{da}^{x}+E_{aN}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{g_{c}(a)N}^{x+1}-E_{kb}^{x+1}+E_{bN}^{x+1}\right)\right\}
	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{aN}^{x}-E_{g_{c}(b)N}^{x}\right)\otimes \left(E_{bN}^{x+1}-E_{g_{c}(a)N}^{x+1}\right)\right\}

@@

Concerning the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x+1})$, the proof is similar and gives
	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{x+1}-E_{aa}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0

@@

>>>>

In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can still host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but where two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$) are present. As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$. This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}. \\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space

@@

	\Omega=\bigotimes_{x=1}^{L} \Omega_{x}

@@

where $\mathcal{L}_{x,x+1}$ is the edge generator defined in \eqref{edgeGenerator} acting on the bond $(x,x+1)$ and $\mathcal{L}_{\text{left}}$ and $\mathcal{L}_{\text{right}}$ are the site generators \eqref{siteGenerator} acting on sites $\{1\}$ and $\{L\}$ with parameters $(\alpha_{a})_{a\in \{1,\ldots,N\}}$ and $(\beta_{a}^{x})_{a\in \{1,\ldots,N\}}$ respectively. 

@@

By Theorem \ref{thm-duality}, the process is dual to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space where two extra-sites with unbounded maximal occupancy $\{0\}$ and $\{L+1\}$ have been added attached to the left of $\{1\}$ and to the right of $\{L+1\}$.
%\begin{equation}\label{stateSpaceDUAL-Chain}	
%	\widetilde{\Omega}=N_{0}^{N}\times\bigotimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N}
Thus, the dual generator reads

@@

where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given from \eqref{siteDualGenerator} absorbing particles from sites $\{1\}$ and $\{L\}$ and putting them at extra-sites $\{0\}$ and $\{L+1\}$ respectively. The duality function reads is \eqref{dualityElements} specified on the chain. 

@@

where $0$ and $L+1$ are the extra-sites.

\begin{comment}
, i.e.
\begin{equation}\label{dualityFunctionChain}
	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
\end{equation}
where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
\end{comment}
The dual process has absorbing boundaries, i.e. all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability. This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following. 
We call $\mu^{NESS}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$. For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\xi}=\sum_{k=1}\delta_{a_{k}}^{x_{k}}$ with $x_{k}\in\{1,\ldots,L\}$ and $a_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$. The following  equalities holds using duality relation \eqref{duality-expectation}:
\begin{equation}\label{ExptationSS}
	\begin{split}
		\mathbb{E}_{\mu^{NESS}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
		\\&=
		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{t_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}(t_{1},\ldots,t_{N},\bm{\xi})
	\end{split}
\end{equation}
where  $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ and where 
\begin{equation}\label{Pass} 
	\mathcal{P}(i_{1},\ldots,i_{N},\bm{\xi})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{0}+(|\xi_{a}|-t_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$. Here we denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x_{k}}$.
The duality function \eqref{dualityElements} computed in the dual configurations $\bm{\xi}$ is given by 
\begin{equation}
	D(\bm{n},\bm{\xi})= \frac{\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}}{(\nu-m+1)}\dt
\end{equation}
Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations. This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known. However, these absorption probabilities fulfil some difference equations that are not easy to solve. For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.

@@

	\mathcal{L}^{rd}=\mathcal{L}_{\text{right}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\mathcal{L}_{\text{right}}^{rd}

@@

The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values are considered at site $L+1$.
\begin{remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{\text{left}}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}. 
\paragraph{Action on the occupation variable}
We only report the final result. The details are written in Appendix \ref{appendix-RD}. For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{1,\ldots,N-1\}$ reads

@@

	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})\co
where $\Delta_{L}n_{x}^{d}= n_{x+1}^{d}+n_{x-1}^{d}-2n_{x}^{d}$. \\For $x=1$ and for all $d\in \{1,\ldots,N-1\}$ we have 

@@

where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu$. These average occupations evolve according to the master equation

@@

\subsubsection{Reversible measure for the reaction-diffusion process} 
The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
	\Lambda_{rev}=\bigtimes_{x=1}^{L}\Lambda_{rev}^{x}
\end{equation}
when for any $a\in\{1,\ldots,N\}$
\begin{equation}\label{reversibilityConditionRD}
	\alpha_{a}=\beta_{a}\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{1,\ldots,N-1\}
\end{equation}
This measure has marginals $\Lambda_{rev}^{x}$ given by 
\begin{equation}
	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)
\end{equation}
where 
\begin{equation}
	p=p_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
\end{equation}
Namely,
\begin{equation}
	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
\end{equation}
This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundaries. %For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
\begin{comment}
\begin{equation}
	\begin{split}
		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{g_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}}\cdots \rho_{N}^{n_{N}^{x}+n_{N}^{x+1}}
		\\
		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{x+1}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots (n_{b}^{x+1}-1)!\cdots (n_{g_{c}(a)}^{x+1}+1)!\ldots n_{N}^{x+1}!}
		\\&
		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}+1}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}+1}
	\end{split}
\end{equation}
that simplifies to

@@

$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}, with the choice of the reservoirs parameters \eqref{boundaryParamRD}.

@@

We need to prove that, for arbitrary $x\in\{1,\ldots,L\}$,
%	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}
%but it is enough of showing 

@@

 We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\exp{(E^{x})}\exp{(E^{x+1})}$ with $E$ defined in \eqref{EquationEx}. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 

@@

	&\left[\left(\sum_{a=1}^{N-1}E_{aN}^{x}\otimes\sum_{a=1}^{N-1}E_{aN}^{x+1}\right), \sum_{d,\ell=1}^{N}\left(E_{g_{c}(\ell)d}^{x}\otimes E_{g_{c}(d)\ell}^{x+1} -E_{dd}^{x}\otimes E_{\ell\ell}^{x+1}\right)\right]

@@

%	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)N}-E_{g_{c}(b)N}^{x}\delta_{ad})-(E_{da}^{x}\delta_{aN}-E_{aN}^{x}\delta_{da})\right)\right. \\ \otimes&\left. \left((E_{kb}^{x+1}\delta_{g_{c}(a)N}-E_{g_{c}N}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{bN}-E_{bN}^{x+1}\delta_{kb})\right)\right\}
%	\\=&
%	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)N}^{x}-E_{da}^{x}+E_{aN}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{g_{c}(a)N}^{x+1}-E_{kb}^{x+1}+E_{bN}^{x+1}\right)\right\}
%	\\=&
	\sum_{a,b=1}^{N-1}\sum_{d,\ell=1}^{N}\left\{\left(E_{dN}^{x}-E_{g_{c}(\ell)N}^{x}\right)\otimes \left(E_{dN}^{x+1}-E_{g_{c}(\ell)N}^{x+1}\right)\right\}

@@

Concerning the commutator between $\mathcal{H}_{x,x+1}^{m}$ the proof is similar and gives
	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN}^{x},\;\sum_{d,\ell=1}^{N}\left(E_{\ell a}^{x}\otimes \mathbbm{1}^{x+1}-E_{dd}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0

@@

\section{One point correlations for the $\nu\geq 1$ case}\label{appendix-1pts-general}
\begin{remark}: In case $|\alpha|=|\beta|=\nu=1$ (when the chain is integrable) we have 
Already for two-point correlations the computations become more involving and hard to solve.
\section{Action on the occupation variable of $\mathcal{L}^{rd}$}\label{appendix-RD}
For all $x\in \{1,\ldots,L-1\}$ and for all $d\in \{1,\ldots,N-1\}$ we have
Using equation \eqref{actionGraphRD} we have \eqref{DifferenceEquation}. Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have \eqref{actionBDLine}.
